Clustering in a hyperbolic model of complex networks.

### 2019-02-21 introduction.tex
new simulation plots in section 1

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/SimulationClusteringCoefficientVariousNu.pdf}
    \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.\label{fig:gamma}}
\end{figure}

@@

\noindent
A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/sim1024ck225n10000a0609nu2rep20.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ 
    (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10000$ and 20 repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a
removable singularity. Again we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but
in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5.pdf}
    \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
\end{figure}

@@

\noindent
A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a
removable singularity. Again we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but
in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
